\begin{center}
    \textbf{\LARGE Acknowledgement}
\end{center}
\noindent
The success of any endeavour is the contributions of several individuals.\smallskip\\

\noindent
I would like to express my sincere gratitude to my supervisor Prof. Shaibal K. Sarkar, for the opportunity to work under his guidance and his invaluable comments and suggestions regarding my work.\smallskip\\

\noindent
I owe a deep sense of gratitude to Mr. Bireswar Mandol for his continuous support in guiding my work and explaining the nuances of research work.\smallskip\\

\noindent
I extend my sincere thanks to Prof. Rangan Banerjee, the Head, Department of Energy Science and Engineering for this opportunity to be part of the M. Sc. - Ph. D. programme.\smallskip\\

\noindent
I extend my gratitude to Prof. Pratibha Sharma, Faculty Advisor for her support and suggestions.\smallskip\\

\noindent
I extend my gratitude to all other members of the laboratory: Dr. Chetan Singh, Dr. Neha Mahuli, Dr.~Anand Selvin S., Dr. Arpan Dhara, Dr. Ansuman Halder, Dr. Dayanand Sutar, Dr. Arpita Sarkar, Ms. Roja Singh, Ms. Vidya Raj, Ms. Sudeshna Ghosh, Mr. Alok Tiwari, Mr. Gaurav Bansode, Mr. Vikas Munya, Ms. Raj Rani, Ms. Shreya Sharma, Ms. Nisha Sarda, Mr. Arya Vikram for their guidance and support.\smallskip\\

\noindent
I am also grateful for the help and support of Ms. Prerna Goradia and Ms. Geetika Bajaj for their help in sample characterisation.\smallskip\\  

\noindent
I am extremely grateful for the continuous encouragement and support of my family, teachers and my friends.\smallskip\\

\noindent
I am grateful for the abundant blessings of the Almighty in every endeavor I have undertaken.