\begin{center}
{\LARGE \textbf{ Declaration}}
\end{center}
I hereby declare that the matter contained in this report titled  \textbf{``Low Temperature Atomic Layer Deposition of {SiO2}"} is an authentic record of research work carried out by me at the \textbf{Devices and Interfaces Lab, Department of Energy Science and Engineering, Indian Institute of Technology Bombay, Mumbai} under the supervision of \textbf{ Prof. Shaibal K. Sarkar}, as part of the \textbf{M. Sc. - Ph. D. Dual Degree Programme} from \textbf{June 2019} to \textbf{November 2019}.\bigskip\\
I declare that this written submission represents my ideas in my own words and where others' ideas or words have been included, I have adequately cited and referenced the original sources. I declare that I have properly and accurately acknowledged all sources used in the production of this report. I also declare that I have adhered to all principles of academic honesty and integrity and have not misrepresented or fabricated or falsified any idea/data/fact/source in my submission. I understand that any violation of the above will be a cause for disciplinary action by the Institute and can also evoke penal action from the sources which have thus not been properly cited or from whom proper permission has not been taken when needed. Any oversight due to error of judgement is regretted.
\vspace{3 cm}

\begin{tabular}{p{80mm}  p{80mm}}
     Date: 20$^{\rm th}$ November 2019 &\makecell[r]{Aditya Chalishazar\\ Place: Mumbai} 
\end{tabular}
